---
title: "Experiment 3 of 4"
output:
  html_document:
    toc: true
    mathjax: default
    template: default
    theme: default
---  

<style>
table, th, td {
    border: 1px grey;
    border-collapse: collapse;
    padding:2px 5px 2px 5px
}  
</style>

```{r loadLibraries, message=FALSE, echo=FALSE}
library(knitr); library(MASS); library(Matrix); library(ggplot2); library(lme4); library(xtable); library(dtplyr); library(lattice); library(LMERConvenienceFunctions); library(grid); library(lmerTest); library(reshape2); library(ggplot2); library(pander); source('summarySEwithin2.R')
```

Experiment Structure: 
Each subject saw 192 trials, being 3 cycles of 64 trials. There were 38 participants. There were 7296 rows in the full data set.

Trial Procedure: 
First an instruction that was a referring expression was presented until participants dismissed it with a key press. Then the squares with dots were presented until the participant responded with a key press, with a 60 second timeout if they did not respond.

In this experiment all instructions used *Number* instruction format.

```{r showInstructions, echo=FALSE, cache=TRUE}
v = c("crisp", "crisp", "vague", "vague")
n = c('number', 'number', 'number', 'number')
t = c("matching", "comparison", "matching", "comparison")
e = c("Choose a square with 6 dots", "Choose a square with fewer than 20 dots", "Choose a square with about 10 dots", "Choose a square with far fewer than 20 dots")
i = data.frame(v, n, t, e)
names(i) = c("vagueness", "instruction format", "selection task", "example instruction")
pander(i, justify=c('center', 'left', 'left', 'left'))
```

```{r showItems, echo=FALSE, cache=TRUE}
items = c(1,2,3,4,5,6,7,8)
i = data.frame(Item = c("1","2","3","4"),
               x = c("06:15:24", "16:25:34", "26:35:44", "36:45:54"))
names(i) = c('Item', 'Numbers of dots')
pander(i, justify=c('center', 'center'))
```

```{r getData, echo=T}
rawdata <- read.delim('e3-data.txt')
```

```{r trimat25sd}
trimdata <- perSubjectTrim.fnc(rawdata, response='RT', subject='Subject', trim = 2.5)$data
rtdata <- trimdata
```

```{r computeSummariesForGraphs, cache=TRUE, message=FALSE, echo=FALSE}
rtdataplot1 <- summarySEwithin2(rtdata, measurevar="RT_log", withinvars=c("Vagueness", "Selection", "Item"), idvar="Subject")
```

```{r e3-rtplot, fig.width=7, fig.height=3, echo=FALSE, dev='pdf'}
dodge = position_dodge(width=NULL)
rtdataplot1$Condition <- as.factor(paste(sep=' ', rtdataplot1$Selection, rtdataplot1$Vagueness))
rtplot=ggplot(rtdataplot1, 
              aes(y=RT_logNormed, x=Item, group=Vagueness, shape=Vagueness, fill=Vagueness)) +
  geom_line() +
  geom_errorbar(width=.2, aes(ymin=RT_logNormed-ci, ymax=RT_logNormed+ci)) +
  geom_point(size=3, col=1, aes(shape=Vagueness)) +
  scale_shape_manual(name="Vagueness", values=c(21,22)) +
  scale_fill_grey(name="Vagueness", start=0, end=1) +
  ggtitle("Response time") +
  ylab("Respone time (log (ms))") + 
  xlab("") +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        legend.key = element_blank(), aspect.ratio=1,
        axis.text.x = element_text(angle = 45, hjust = 1),
        plot.background=element_rect(fill=NA, color='white'),
        strip.background=element_blank()) +
  facet_grid(~Selection) 
rtplot
```

```{r rtlmer, cache=TRUE}
rtlmer = lmerTest::lmer(data=rtdata,
                        RT_log ~ c_Vag * c_Sel + c_Itm +
                          (1 + c_Vag * c_Sel + c_Itm | Subject))
```

```{r rtlmersummaryxtable, results='asis', cache=TRUE, echo=F}
print(
  xtable(
    summary(rtlmer)$coefficients[,-3], 
    display=c("s","f","f","f","f"),
    digits=c(0,2,2,1,3),
    caption="Response time model"),
  caption.placement="top", 
  type='html')
```

```{r seplmersforcomparison, results='asis', cache=TRUE, echo=-3}
comparisonOnly <- subset(rtdata, subset=Selection=='Comparison')
comparisonOnlylm <- lmerTest::lmer(data=comparisonOnly, RT_log ~ c_Vag + c_Itm + (1 + c_Vag + c_Itm | Subject))
print(
  xtable(
    summary(comparisonOnlylm)$coefficients[,-3], 
    display=c("s","f","f","f","f"),
    digits=c(0,2,2,1,3),
    caption="Response time model: Comparison only"),
  caption.placement="top", 
  type='html')
```

```{r seplmersformatching, results='asis', cache=TRUE, echo=-3}
matchingOnly <- subset(rtdata, subset=Selection=='Matching')
matchingOnlylm <- lmerTest::lmer(data=matchingOnly, RT_log ~ c_Vag + c_Itm + (1 + c_Vag + c_Itm | Subject))
print(
  xtable(
    summary(matchingOnlylm)$coefficients[,-3], 
    display=c("s","f","f","f","f"),
    digits=c(0,2,2,1,3),
    caption="Response time model: Matching only"),
  caption.placement="top", 
  type='html')
```
